### 2016-07-18 paper/algorithms.tex
darcy fwd, small paper edits, stashing notes

	$\epsilon_0=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_0})(\Lambda_0)+\mathcal M_{HF}(\Psi_{MF_0})-\mathcal M_{MF_0}(\Psi_{MF_0})$}
	\State{Calculate QoI $I(q_{MF_0},u_{MF_0})$}
	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/I(q_{MF_i},u_{MF_i})|>$ \texttt{errTol}}
		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ (see section~\cref{sect:error_est_localize}) and use this decomposition to guide \par\hskip\algorithmicindent formation of new mixed-fidelity model MF$_{i+1}$\end{varwidth}}
		\State{$i\gets i+1$}
		\State{Solve for stationary point $\Psi_{MF_i}$ of augmented Lagrangian $\mathcal{M}_{MF_i}$}
		\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_i}$, for

@@

Algorithm~\cref{alg:refSeries} can be naturally extended to an online-offline setting, where a multi-fidelity model adaptive constraint can be generated for a given data set in the offline phase. In the online phase, additional data points are added to the data set, and instead of solving the complete inverse problem with all the data points, and the high-fidelity constraints, an iterative algorithm can be initiated using the multi-fidelity representation developed in the offline phase. The adaptive procedure, with the supplementary adjoint can be used to adapt the preexisting multi-fidelity representation to the new data points.  
%
\alglanguage{pseudocode}
\begin{algorithm}[h!]
\small
\caption{An algorithm to adapt a pre-computed mixed-fidelity model to new data.}
\label{alg:refonoff}
\begin{algorithmic}[1]
\State{Define maximum acceptable absolute relative QoI error \texttt{errTol}}
\State{Given a data set $d_1 \in \R^{n_{d_1}}$, and an adaptively build a mixed-fidelity model for low error in the QoI, use Algorithm~\ref{} to build a MF model MF$_1$} 
\Procedure{$\texttt{Online}$}{HF model, MF model MF$_1$, \texttt{errTol}, $d_2 \in \R^{n_{d_2}}$}
	\State{$i\gets1$}
	\State{Solve for stationary point $\Psi_{MF_1}$ of augmented Lagrangian $\mathcal{M}_{MF_1}$ formed using new data set $d_2$}
	\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_1}$, for \par\hskip\algorithmicindent supplementary adjoint $\Lambda_1$ (see \cref{eq:superAdjEq})}
	\State{Compute QoI error estimate

	$\epsilon_0=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_1})(\Lambda_1)+\mathcal M_{HF}(\Psi_{MF_1})-\mathcal M_{MF_1}(\Psi_{MF_1})$}
	\State{Calculate QoI $I(q_{MF_1},u_{MF_1})$}
	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/I(q_{MF_i},u_{MF_i})|>$ \texttt{errTol}}
		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ (see section~\cref{sect:error_est_localize}) and use this decomposition to guide \par\hskip\algorithmicindent formation of new mixed-fidelity model MF$_{i+1}$\end{varwidth}}
		\State{$i\gets i+1$}
		\State{Solve for stationary point $\Psi_{MF_i}$ of augmented Lagrangian $\mathcal{M}_{MF_i}$}
		\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_i}$, for

@@

		$\quad\quad \epsilon_i=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_i})(\Lambda_i)+\mathcal M_{HF}(\Psi_{MF_i})-\mathcal M_{MF_i}(\Psi_{MF_i})$}
		\State{Calculate QoI $I(q_{MF_i},u_{MF_i})$}
	\EndWhile \\
\Return{QoI estimate $I(q_{MF_i},u_{MF_i})$ for the new data set $d_2$}
\EndProcedure
\Statex
\end{algorithmic}
\end{algorithm}
%
Algorithm~\cref{alg:refonoff} lends itself to a quasi-incremental data assimilation approach, where the data set $d_2$ is an augmentation of the original set $d_1$. In such a situation, we expect that the model refinement will be concentrated around the new data points, that also inform the QoI. Thus, in the online phase, even though the inverse problem will be solved with all data points, the use of high-fidelity models will be limited, and the bulk of the computation (computing the auxilary variables, and supplementary adjoint) will be focused on identifying those new data points, which have the maximum impact on the QoI.

Algorithm~\cref{alg:refSeries} is applicable to a large class of models. The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, be a reduced-order model, or have a reduced parameter space. The two models could also correspond to two levels of mesh-refinement, though in this case the method described in~\cite{BecVex05} could be more efficient, since interpolation could be used to estimate $\Psi_{HF}-\Psi_{LF}$ instead. The derived error estimate is not applicable to all models, however. The two models have to be expressed in a weak form, so this cannot be applied to, for example, a model of chemical reactions using kinetic Monte Carlo. We need some degree of compatibility between the two models; namely, we assume that $\Psi_{LF}$ will be in a space admissible to $\mathcal{M}'_{HF,\Psi}$, and that the QoI functional $I$ is applicable to both $(q_{HF},u_{HF})$ and $(q_{LF},u_{LF})$.
%------------------------------------------------------------------------------------------------------------------------%
\subsubsection{Error Estimate Localization}\label{sec:errLocal}
%------------------------------------------------------------------------------------------------------------------------%
Algorithm~\cref{alg:refSeries} does not require a specific method for localizing the error estimate. A na\"{i}ve approach would be to write the error estimate as a sum of integrals over elements and their boundaries, and calculate the error contribution by each element as the integral over that element. While simple, this method can lead to non-zero error contributions from elements in which the high-fidelity model is already being used, making the error decomposition more difficult to interpret and use for refinement.

>>>>

	$\epsilon_0=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_0})(\Lambda_0)+\mathcal M_{HF}(\Psi_{MF_0})-\mathcal M_{MF_0}(\Psi_{MF_0})$}
	\State{Calculate QoI $I(q_{MF_0},u_{MF_0})$}
	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/I(q_{MF_i},u_{MF_i})|>$ \texttt{errTol}}
		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ (see \cref{sec:errLocal}) and use this decomposition to guide \par\hskip\algorithmicindent formation of new mixed-fidelity model MF$_{i+1}$\end{varwidth}}
		\State{$i\gets i+1$}
		\State{Solve for stationary point $\Psi_{MF_i}$ of augmented Lagrangian $\mathcal{M}_{MF_i}$}
		\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_i}$, for

@@

\Cref{alg:refSeries} can be naturally extended to an online-offline setting, where a multi-fidelity model adaptive constraint can be generated for a given data set in the offline phase. In the online phase, additional data points are added to the data set, and instead of solving the complete inverse problem with all the data points, and the high-fidelity constraints, an iterative algorithm can be initiated using the multi-fidelity representation developed in the offline phase. The adaptive procedure, with the supplementary adjoint can be used to adapt the preexisting multi-fidelity representation to the new data points.  
%
\alglanguage{pseudocode}
\begin{algorithm}[h!]
\small
\caption{An algorithm to adapt a pre-computed mixed-fidelity model to new data.}
\label{alg:refonoff}
\begin{algorithmic}[1]
\State{Define maximum acceptable absolute relative QoI error \texttt{errTol}}
\State{Given a data set $d_1 \in \R^{n_{d_1}}$, and an adaptively build a mixed-fidelity model for low error in the QoI, use \cref{alg:refSeries} to build a MF model MF$_1$} 
\Procedure{$\texttt{Online}$}{HF model, MF model MF$_1$, \texttt{errTol}, $d_2 \in \R^{n_{d_2}}$}
	\State{$i\gets1$}
	\State{Solve for stationary point $\Psi_{MF_1}$ of augmented Lagrangian $\mathcal{M}_{MF_1}$ formed using new data set $d_2$}
	\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_1}$, for \par\hskip\algorithmicindent supplementary adjoint $\Lambda_1$ (see \cref{eq:superAdjEq})}
	\State{Compute QoI error estimate

	$\epsilon_0=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_1})(\Lambda_1)+\mathcal M_{HF}(\Psi_{MF_1})-\mathcal M_{MF_1}(\Psi_{MF_1})$}
	\State{Calculate QoI $I(q_{MF_1},u_{MF_1})$}
	\While{$i<$ \texttt{maxIter} and $|\epsilon_i/I(q_{MF_i},u_{MF_i})|>$ \texttt{errTol}}
		\State{\begin{varwidth}[t]{\linewidth}Localize $\epsilon_i$ (see \cref{sec:errLocal}) and use this decomposition to guide \par\hskip\algorithmicindent formation of new mixed-fidelity model MF$_{i+1}$\end{varwidth}}
		\State{$i\gets i+1$}
		\State{Solve for stationary point $\Psi_{MF_i}$ of augmented Lagrangian $\mathcal{M}_{MF_i}$}
		\State{Solve QoI error adjoint equation, linearized about $\Psi_{MF_i}$, for

@@

		$\quad\quad \epsilon_i=-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{MF_i})(\Lambda_i)+\mathcal M_{HF}(\Psi_{MF_i})-\mathcal M_{MF_i}(\Psi_{MF_i})$}
		\State{Calculate QoI $I(q_{MF_i},u_{MF_i})$}
	\EndWhile \\
\Return{QoI estimate $I(q_{MF_i},u_{MF_i})$ for the new data set $d_2$}
\EndProcedure
\Statex
\end{algorithmic}
\end{algorithm}
%
\Cref{alg:refonoff} lends itself to a quasi-incremental data assimilation approach, where the data set $d_2$ is an augmentation of the original set $d_1$. In such a situation, we expect that the model refinement will be concentrated around the new data points, that also inform the QoI. Thus, in the online phase, even though the inverse problem will be solved with all data points, the use of high-fidelity models will be limited, and the bulk of the computation (computing the auxilary variables, and supplementary adjoint) will be focused on identifying those new data points, which have the maximum impact on the QoI.

\Cref{alg:refSeries} is applicable to a large class of models. The lower-fidelity model could, for example, be a simplified model including fewer physical phenomena, be a reduced-order model, or have a reduced parameter space. The two models could also correspond to two levels of mesh-refinement, though in this case the method described in~\cite{BecVex05} could be more efficient, since interpolation could be used to estimate $\Psi_{HF}-\Psi_{LF}$ instead. The derived error estimate is not applicable to all models, however. The two models have to be expressed in a weak form, so this cannot be applied to, for example, a model of chemical reactions using kinetic Monte Carlo. We need some degree of compatibility between the two models; namely, we assume that $\Psi_{LF}$ will be in a space admissible to $\mathcal{M}'_{HF,\Psi}$, and that the QoI functional $I$ is applicable to both $(q_{HF},u_{HF})$ and $(q_{LF},u_{LF})$.
%------------------------------------------------------------------------------------------------------------------------%
\subsubsection{Error Estimate Localization}\label{sec:errLocal}
%------------------------------------------------------------------------------------------------------------------------%
Algorithm~\cref{alg:refSeries} does not require a specific method for localizing the error estimate. A na\"{i}ve approach would be to write the error estimate as a sum of integrals over elements and their boundaries, and calculate the error contribution by each element as the integral over that element. While simple, this method can lead to non-zero error contributions from elements in which the high-fidelity model is already being used, making the error decomposition more difficult to interpret and use for refinement.

### 2016-07-18 paper/numerical_experiments.tex
darcy fwd, small paper edits, stashing notes

We now present the results of solving the inference problem using \cref{alg:refSeries}, with a relative error tolerance of $0.1\%$. At each iteration, we choose the $10\%$ of the basis functions with the largest error for model refinement; since each linear Lagrange basis function has eight elements in its support, the number of additional elements marked for refinement in each iteration may be larger. All simulations are run on a single processor; we use the default nonlinear solver in \texttt{libMesh} (Newton's method with Brent line-search), and linear solves are performed using PETSC's GMRES solver\footnote{\red{Do we need more detail on the flags?}}. \Cref{tab:ref3D} shows the runtime and error at the end of each iteration. For the high-fidelity inverse problem, the Newton solver does not converge with a constant initial guess ($(p,u,z)=(0,5,0)$); instead, we solve the low-fidelity inverse problem and use its solution as the initial guess for the high-fidelity inverse problem. Each iteration of the adaptive algorithm uses the solution of the previous iteration as its initial guess. The runtime for each iteration of the adaptive algorithm is the total runtime, from the beginning of the adaptivity to the calculation of the error estimate for that iteration.
%
\begin{table}[htbp]
\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.001$ and $10\%$ of basis function marked for refinement per iteration; relative errors are with respect to true high-fidelity QoI.}
\label{tab:ref3D}
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative & Total \\ 
& & & (Estimated) & (Actual) & Error (Actual) & Time (s) \\ \hline
LF   & 0    & 1068856 & -400845 & -521438 & -95.2534 & 160 \\
MF01 & 16.7 & 577582  & -22143  & -30164  & -5.5098  & 1110 \\
MF02 & 29.0 & 548904  & 1200    & -1486   & -0.2711  & 1800 \\
MF03 & 42.3 & 547773  & 176     & -355    & -0.0645  & 2220 \\ %even if rel err is vs predicted I_HF, goes below 0.1% here first
HF   & 100  & 547418  & --      & 0       & 0        & 350 \\ \hline
\end{tabular}
\end{table}
%
Compared to the previous examples in \cref{sec:cdvcdr} with similar physics in the pair of models, we notice that in this case the estimated relative error in the later iterations is similar to the actual relative error in magnitude, but not in sign. This is likely due to the additional difference in the diffusive coefficient of the two models in this case. The sign difference does not, however, prevent the algorithm from finding a mixed-fidelity model for which the QoI matches the high-fidelity QoI to within the chosen tolerance. %what happens if you go on forever? the sign corrects itself in the next two iterations, and then becomes wrong again (last few iterations of 5% rate run are correct sign though...)...also final all-HF QoI doesn't quite agree with invHF version (agrees to five sig figs; running both rates of adaptive to 100% HF gives same qoi to 8 sig figs)...also 'continuation' this way is faster (4600 with 10% rate, but 6600 with 5% rate) than the other continuation schemes you tried...if we want to open this can of worms, will probably have to do more in-depth search of existing continuation algorithms...

@@

\Cref{tab:ref3D_dainty} shows the runtime and error at the end of each of these iterations, and \cref{fig:divvy3D_dainty} shows the domain divisions for the six corresponding mixed-fidelity models.
%
\begin{table}
\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.001$ and $5\%$ of basis function marked for refinement per iteration; relative errors are with respect to true high-fidelity QoI.}
\label{tab:ref3D_dainty}
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative & Total \\ 
& & & (Estimated) & (Actual) & Error (Actual) & Time (s) \\ \hline
LF   & 0    & 1068856 & -400845 & -521438 & -95.2534 & 160 \\
MF01 & 9.27 & 613419  & -40789  & -66001  & -12.0564 & 1040 \\
MF02 & 16.9 & 558523  & 1162    & -11105  & -2.0282  & 1860 \\
MF03 & 23.7 & 550323  & 2510    & -2905   & -0.5303  & 2420 \\
MF04 & 30.4 & 548225  & 1658    & -807    & -0.1471  & 2970 \\
MF05 & 37.2 & 547744  & 655     & -326    & -0.0591  & 3309 \\
MF06 & 44.6 & 547532  & 194     & -114    & -0.0205  & 3642 \\ %even if rel err is vs predicted I_HF, goes below 0.1% here first
HF   & 100  & 547418  & --      & 0       & 0        & 350 \\ \hline
\end{tabular}
\end{table}
%
\begin{figure}[htbp]
\centering
\subfloat[MF$_1$]{
\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy1_whitebg_puff.png} 
\label{fig:ref3d_dainty1}
}
\subfloat[MF$_2$]{
\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy2_whitebg_puff.png} 
\label{fig:ref3d_dainty2}
}
\subfloat[MF$_3$]{
\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy3_whitebg_puff.png} 
} \\
\subfloat[MF$_4$]{
\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy4_whitebg_puff.png} 
}
\subfloat[MF$_5$]{
\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy5_whitebg_puff.png} 
}
\subfloat[MF$_6$]{
\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy6_whitebg_puff.png} 
}
\caption{Domain division for mixed-fidelity models: low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion (intermediate colors due to transparency indicate a mix of the two models along the line of sight); $x_3$ direction scaled for clarity.}
\label{fig:divvy3D_dainty}
\end{figure} 
%
We again observe that the estimated relative error in the later iterations is similar to the actual relative error in magnitude, but not in sign. It can also be seen in \cref{fig:ref3d_dainty1} that the largest error first comes from the QoI region and area below it, and the observations. Similarly to the examples in \cref{sec:cdvcdr}, of the observations, refinement is least necessary around the ones furthest downstream of the QoI region.

>>>>

We now present the results of solving the inference problem using \cref{alg:refSeries}, with a relative error tolerance of $0.1\%$. At each iteration, we choose the $10\%$ of the basis functions with the largest error for model refinement; since each linear Lagrange basis function has eight elements in its support, the number of additional elements marked for refinement in each iteration may be larger. All simulations are run on a single processor; we use the default nonlinear solver in \texttt{libMesh} (Newton's method with Brent line-search), and linear solves are performed using PETSC's GMRES solver\footnote{\red{Do we need more detail on the flags?}}. \Cref{tab:ref3D} shows the runtime and error at the end of each iteration. For the high-fidelity inverse problem, the Newton solver does not converge with a constant initial guess ($(p,u,z)=(0,5,0)$); instead, we solve the low-fidelity inverse problem and use its solution as the initial guess for the high-fidelity inverse problem. Each iteration of the adaptive algorithm uses the solution of the previous iteration as its initial guess. The runtime for each iteration of the adaptive algorithm is the total runtime, from the beginning of the adaptivity to the calculation of the error estimate for that iteration.
%
\begin{table}[htbp]
\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.001$ and $10\%$ of basis function marked for refinement per iteration; relative errors are with respect to true high-fidelity QoI.}
\label{tab:ref3D}
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative & Total \\ 
& & & (Estimated) & (Actual) & Error (Actual) & Time (s) \\ \hline
LF   & 0    & 1068856 & -400845 & -521438 & -95.2534 & 160 \\
MF01 & 16.7 & 577582  & -22143  & -30164  & -5.5098  & 1110 \\
MF02 & 29.0 & 548904  & 1200    & -1486   & -0.2711  & 1800 \\
MF03 & 42.3 & 547773  & 176     & -355    & -0.0645  & 2220 \\ %even if rel err is vs predicted I_HF, goes below 0.1% here first
HF   & 100  & 547418  & --      & 0       & 0        & 440 \\ \hline
\end{tabular}
\end{table}
%
Compared to the previous examples in \cref{sec:cdvcdr} with similar physics in the pair of models, we notice that in this case the estimated relative error in the later iterations is similar to the actual relative error in magnitude, but not in sign. This is likely due to the additional difference in the diffusive coefficient of the two models in this case. The sign difference does not, however, prevent the algorithm from finding a mixed-fidelity model for which the QoI matches the high-fidelity QoI to within the chosen tolerance. %what happens if you go on forever? the sign corrects itself in the next two iterations, and then becomes wrong again (last few iterations of 5% rate run are correct sign though...)...also final all-HF QoI doesn't quite agree with invHF version (agrees to five sig figs; running both rates of adaptive to 100% HF gives same qoi to 8 sig figs)...also 'continuation' this way is faster (4600 with 10% rate, but 6600 with 5% rate) than the other continuation schemes you tried...if we want to open this can of worms, will probably have to do more in-depth search of existing continuation algorithms...

@@

\Cref{tab:ref3D_dainty} shows the runtime and error at the end of each of these iterations, and \cref{fig:divvy3D_dainty} shows the domain divisions for the six corresponding mixed-fidelity models.
%
\begin{table}
\caption{Runtime and relative errors of adaptive algorithm iterations given relative error tolerance of $0.001$ and $5\%$ of basis function marked for refinement per iteration; relative errors are with respect to true high-fidelity QoI.}
\label{tab:ref3D_dainty}
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Case} & \multirow{2}{*}{$\%$HF} & \multirow{2}{*}{QoI} & Error & Error & $\%$ Relative & Total \\ 
& & & (Estimated) & (Actual) & Error (Actual) & Time (s) \\ \hline
LF   & 0    & 1068856 & -400845 & -521438 & -95.2534 & 160 \\
MF01 & 9.27 & 613419  & -40789  & -66001  & -12.0564 & 1040 \\
MF02 & 16.9 & 558523  & 1162    & -11105  & -2.0282  & 1860 \\
MF03 & 23.7 & 550323  & 2510    & -2905   & -0.5303  & 2420 \\
MF04 & 30.4 & 548225  & 1658    & -807    & -0.1471  & 2970 \\
MF05 & 37.2 & 547744  & 655     & -326    & -0.0591  & 3309 \\
MF06 & 44.6 & 547532  & 194     & -114    & -0.0205  & 3642 \\ %even if rel err is vs predicted I_HF, goes below 0.1% here first
HF   & 100  & 547418  & --      & 0       & 0        & 440 \\ \hline
\end{tabular}
\end{table}
%
\begin{figure}[htbp]
\centering
\subfloat[MF$_1$]{
\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy1_whitebg_puff.png} 
\label{fig:ref3d_dainty1}
}
\subfloat[MF$_2$]{
\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy2_whitebg_puff.png} 
\label{fig:ref3d_dainty2}
}
\subfloat[MF$_3$]{
\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy3_whitebg_puff.png} 
} \\
\subfloat[MF$_4$]{
\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy4_whitebg_puff.png} 
}
\subfloat[MF$_5$]{
\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy5_whitebg_puff.png} 
}
\subfloat[MF$_6$]{
\includegraphics[width=0.31\textwidth]{series3D/run_0p05/divvy6_whitebg_puff.png} 
}
\caption{Domain division for mixed-fidelity models: low-fidelity convection-diffusion model used in red portion, high-fidelity convection-diffusion-reaction model used in blue portion (intermediate colors due to transparency indicate a mix of the two models along the line of sight); $x_3$ direction scaled for clarity.}
\label{fig:divvy3D_dainty}
\end{figure} 
%
We again observe that the estimated relative error in the later iterations is similar to the actual relative error in magnitude, but not in sign. It can also be seen in \cref{fig:ref3d_dainty1} that the largest error first comes from the QoI region and area below it, and the observations. Similarly to the examples in \cref{sec:cdvcdr}, of the observations, refinement is least necessary around the ones furthest downstream of the QoI region.
